\documentclass[12pt,letterpaper]{hmcpset}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{amsmath}

% info for header block in upper right hand corner
\name{ --- }
\class{Math 40 - Section ---}
\assignment{Spanning Sets, Linear Independence, and Matrix Operations}
\duedate{Tuesday, February 2, 2016}

\newcommand{\pn}[1]{\left( #1 \right)}
\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\bk}[1]{\left[ #1 \right]}

\newcommand{\vb}{\mathbf{v}}
\newcommand{\ub}{\mathbf{u}}
\newcommand{\fx}{f \left( x \right) =}
\newcommand*\LH{\ensuremath{\overset{\kern2pt L'H}{=}}}
\renewcommand{\labelenumi}{{(\alph{enumi})}}

\begin{document}

\problemlist{2.3.\{8, 12, 24, 42\}, 3.1.\{26, 38\}}

% 2.3.8 %
\begin{problem}[2.3.8]
Determine if the vector $\mathbf{b}$ is in the span of the columns of the matrix $A$. $$ A = \begin{bmatrix}
    1 & 2 & 3\\
    5 & 6 & 7\\
    9 & 10 & 11
\end{bmatrix}\text{, } \mathbf{b} =\begin{bmatrix}
	4\\
	8\\
    12
\end{bmatrix}$$

\end{problem}

\begin{solution}
\vfill
\end{solution}

\newpage

% 2.3.12 %
\begin{problem}[2.3.12]

Show that $\mathbb{R}^3 = \text{span}\left( \begin{bmatrix}
	1\\
	1\\
	0
\end{bmatrix}\text{, }\begin{bmatrix}
	1\\
	2\\
	3
\end{bmatrix}\text{, }\begin{bmatrix}
	2\\
	1\\
	-1
\end{bmatrix}\right).$

\end{problem}

\begin{solution}
\vfill
\end{solution}
\newpage

% 2.3.24 %
\begin{problem}[2.3.24]

Use the method of Example 2.23 and Theorem 2.6 to determine if the sets of vectors are linearly independent. If the answer can be determined by inspection (i.e., without calculation), state why. For any sets that are linearly dependent, find a dependence relationship among the vectors.$$\begin{bmatrix}
	2\\
	2\\
	1
\end{bmatrix}\text{, }\begin{bmatrix}
	3\\
	1\\
	2
\end{bmatrix}\text{, }\begin{bmatrix}
	1\\
	-5\\
	2
\end{bmatrix}$$

\end{problem}

\begin{solution}
\vfill
\end{solution}
\newpage

% 2.2.28 %
\begin{problem}[2.2.28]

Use the method of Example 2.23 and Theorem 2.6 to determine if the sets of vectors are linearly independent. If the answer can be determined by inspection (i.e., without calculation), state why. For any sets that are linearly dependent, find a dependence relationship among the vectors.$$\begin{bmatrix}
	-1\\
	1\\
	2\\
	1
\end{bmatrix}\text{, }\begin{bmatrix}
	3\\
	2\\
	2\\
	4
\end{bmatrix}\text{, }\begin{bmatrix}
	2\\
	3\\
	1\\
	-1
\end{bmatrix}$$

\end{problem}

\begin{solution}
\vfill
\end{solution}
\newpage

% 2.3.42 %
\begin{problem}[2.3.42]

\begin{enumerate}
	\item
		If the columns of an $n \times n$ matrix $A$ are linearly independent as vectors in $\mathbb{R}^n$, what is the rank of $A$? Explain.
	\item
		If the rows of an $n \times n$ matrix $A$ are linearly independent as vectors in $\mathbb{R}^n$, what is the rank of $A$? Explain.
\end{enumerate}

\end{problem}

\begin{solution}
\vfill
\end{solution}
\newpage

% 3.1.26 %
\begin{problem}[3.1.26]

Use the matrix-column representation of the product to write each column of $BA$ as a linear combination of the columns of $B$.\\

$$A = \begin{bmatrix}
        1 & 0 & -2 \\
        -3 & 1 & 1 \\
        2 & 0 & -1
      \end{bmatrix} \hspace{0.5in} B = \begin{bmatrix}
	2 & 3 & 0 \\
	1 & -1 & 1 \\
	-1 & 6 & 4
    \end{bmatrix}$$\\

\end{problem}

\begin{solution}
\vfill
\end{solution}
\newpage

% 3.1.38 %
\begin{problem}[3.1.38]

Let $A = \begin{bmatrix}
		\cos{\theta} & -\sin{\theta}\\
		\sin{\theta} & \cos{\theta}
	\end{bmatrix}$.\\
	\begin{enumerate}
		\item
			Show that $A^2 = \begin{bmatrix}
				\cos{2\theta} & -\sin{2\theta}\\
				\sin{2\theta} & \cos{2\theta}
				\end{bmatrix}$.
		\item
			Prove, by mathematical induction, that $$A^n = \begin{bmatrix}
				\cos{n\theta} & -\sin{n\theta}\\
				\sin{n\theta} & \cos{n\theta}
				\end{bmatrix} \text{ for } n \geq 1$$
	\end{enumerate}
\end{problem}

\begin{solution}
\vfill
\end{solution}

\end{document}
